Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-05-08 analysis/paper/paper.qmd
hided the cv tests for impact of sample size
Edit repetitive word.

We also explored spatial patterns using 16 geographical zones based on geographical characteristics including inland, coastal areas, major rivers, islands, and major mountain ranges in addition to ecological information including temperature and precipitation [@lee2008relationship]. The sites in our sample occur in 14 of these zones: Imjin river basin (IRB), Metropolitan (MP), Central inland (CI), Kangwon coastal (KC), Choongnam coastal (CC), Southwestern inland (SWI), Upper Nagdong river basin (UNRB), WoolYoung coastal (WYC), Western Cholla (WC), Southern mountain (SM), Southeastern inland (SEI), Hyungsan Taewha coastal (HTC), Western south coastal (WSC), and Eastern south coastal (ESC). Then, we used longitude and latitude to locate individual assemblages and examined TCSA values for each zone. We are fully acknowledged that modern eco-regional maps do not fully resemble the Pleistocene landscape in which the points were made and used. However, in the absence of detailed paleoenvironmental information, we thought it is still meaningful to adapt the modern information of vegetation and geography by assuming that some environmental factors such as  altitude, slope, drainage, hydrology, and bedrock are relatively stable over time. And those factors enable us to think that the modern vegetation patterns can be used to make reasonable references about the past.

@@

plot_grid(  tcsa_all_stage_plot,
  tcsa_all_raw_plot,
tcsa_all_ass_plot,
 tcsa_all_veg_plot, 
  tcsa_all_geo_plot,
ncol =2,
label_size = 1)

>>>>

We also explored spatial patterns using 16 geographical zones based on geographical characteristics including inland, coastal areas, major rivers, islands, and major mountain ranges in addition to ecological information including temperature and precipitation [@lee2008relationship]. The sites in our sample occur in 14 of these zones: Imjin river basin (IRB), Metropolitan (MP), Central inland (CI), Kangwon coastal (KC), Choongnam coastal (CC), Southwestern inland (SWI), Upper Nagdong river basin (UNRB), WoolYoung coastal (WYC), Western Cholla (WC), Southern mountain (SM), Southeastern inland (SEI), Hyungsan Taewha coastal (HTC), Western south coastal (WSC), and Eastern south coastal (ESC). Then, we used longitude and latitude to locate individual assemblages and examined TCSA values for each zone. We are well aware that modern eco-regional maps do not fully resemble the Pleistocene landscape in which the points were made and used. However, in the absence of detailed paleoenvironmental information, we thought it is still meaningful to adapt the modern information of vegetation and geography by assuming that some environmental factors such as  altitude, slope, drainage, hydrology, and bedrock are relatively stable over time. And those factors enable us to think that the modern vegetation patterns can be used to make reasonable references about the past.

@@

# plot_grid(  tcsa_all_stage_plot,
#   tcsa_all_raw_plot,
# tcsa_all_ass_plot,
#  tcsa_all_veg_plot, 
#   tcsa_all_geo_plot,
# ncol =2,
# label_size = 1)
